---
title: "DescribeThisDataset"
output: html_document
params:
  Dataset: NULL
  Individual: TRUE
  ColumnN: NULL
  HeadOfDataset: FALSE
  StructureOfDataset: FALSE
  NameOfDataset: "Dataset"
  Cols: list()
  ColsFormat: list()
  DetailInformation: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include=FALSE}
  if (!require("ggplot2")) install.packages("ggplot2") 
  library(ggplot2)
  if (!require("data.table")) install.packages("data.table")
  library(data.table)
```

```{r Diagnosi, echo=FALSE}
  Dataset= params$Dataset
  Individual= params$Individual
  HeadOfDataset= params$HeadOfDataset
  StructureOfDataset= params$StructureOfDataset
  NameOfDataset= params$NameOfDataset
  Cols=params$Cols
  ColsFormat=params$ColsFormat
  DetailInformation=params$DetailInformation
  
  ## Datatable
  if(!is.data.table(Dataset)){
    Dataset=data.table(Dataset)
  }
  
  ## Dimension of the dataset
  Database_dim<-dim(Dataset)
  n_of_observations<-Database_dim[1]
  n_of_variables<-Database_dim[2]
  
  ## Table Output
  row_of_df_output=4
  df_output<- data.frame(matrix(ncol = n_of_variables, nrow = row_of_df_output))
  colnames(df_output)<-names(Dataset)
  rownames(df_output)<-c("missing_count", "missing_percent", "unique_count", "unique_rate")
  
  for( i in names(Dataset)){
    df_output[1,i]=sum(is.na(Dataset[,get(i)]))
    df_output[2,i]=round((sum(is.na(Dataset[,get(i)]))/n_of_observations)*100, 2)
    df_output[3,i]=length(unique(Dataset[,get(i)]))
    df_output[4,i]=round(length(unique(Dataset[,get(i)]))/n_of_observations, 2)
  }
```

```{r check, echo=FALSE}
## check that Cols and ColsFormat is a list 
if (!inherits(Cols, "list")){  
  stop("parameter Cols must be a list")
}

if (!inherits(ColsFormat, "list")){  
  stop("parameter ColsFormat must be a list")
}

## check if Cols and ColsFormat have the same length
if (length(Cols)!=length(ColsFormat)){  
  stop("parameter Cols must have the same length as ColsFormat")
}
```

This is a description of  **`r NameOfDataset`**, this dataset is composed by `r n_of_observations` observations of  `r n_of_variables` variables.

### Diagnosi
```{r DF_output, include=TRUE, echo=FALSE}
knitr::kable(df_output, caption = "Missing and Unique diagnosi")
```
 
```{r Head, include=TRUE, echo=FALSE}
  if(HeadOfDataset==TRUE){
    knitr::kable(head(Dataset),  caption = "Head of the dataset")
  }
```

`r if(StructureOfDataset){"This is the structure of the dataset"}`
```{r Structure, include=TRUE, echo=FALSE}
  if(StructureOfDataset){
    str(Dataset)
  }
```

```{r Boolean Definition, include=TRUE, echo=FALSE}
  nVars_nForm = length(Cols)==0 & length(ColsFormat)==0 
  Vars_nForm = length(Cols)!=0 & length(ColsFormat)==0 
  Vars_Form_nDet = length(Cols)!=0 & length(ColsFormat)!=0 & !DetailInformation 
  Vars_Form_Det = length(Cols)!=0 & length(ColsFormat)!=0 & DetailInformation 
```

`r if(nVars_nForm){"The variables and their format are not specified"}`
```{r Vars and Format non specified, include=TRUE, echo=FALSE}
if(nVars_nForm){  
  for(i in names(Dataset)){
    if(df_output["unique_count",i]<=10){
      p = ggplot(Dataset, aes_string(x=i))+
           geom_bar()+
           ggtitle(paste0("Bar graph of ",i, ":"))
      suppressMessages(print(p))
    }
    if(df_output["unique_count",i]>10 & df_output["unique_count",i]<=50){
      p = ggplot(Dataset, aes_string(x=i))+
            geom_histogram()+
            ggtitle(paste0("Histogram of ",i, ":"))
      suppressMessages(print(p))
    }
    if(df_output["unique_count",i]>50){
      p = ggplot(Dataset, aes_string(x=i))+
           geom_density()+
           ggtitle(paste0("Density of ",i, ":"))
      suppressMessages(print(p))
      }
  }
}
```

`r if(Vars_nForm){"The format of the variable is not specified"}`
```{r Vars specified and Format non specified, include=TRUE, echo=FALSE}
if(Vars_nForm){
  for(i in Cols){
        if(df_output["unique_count",i]<=10){
          p = ggplot(Dataset, aes_string(x=i))+
               geom_bar()+
               ggtitle(paste0("Bar graph of ",i, ":"))
          suppressMessages(print(p))
        }
        if(df_output["unique_count",i]>10 & df_output["unique_count",i]<=50){
          p = ggplot(Dataset, aes_string(x=i))+
              geom_histogram()+
              ggtitle(paste0("Histogram of ",i, ":"))
          suppressMessages(print(p))
        }
        if(df_output["unique_count",i]>50){
          p = ggplot(Dataset, aes_string(x=i))+
               geom_density()+
               ggtitle(paste0("Density of ",i, ":"))
          suppressMessages(print(p))
        }
  }
}
```

`r if(Vars_Form_Det){"The variables to be described and their formats are specified"}`
```{r Vars specified and Format specified and Detailed, results = "asis", include=TRUE, echo=FALSE}
if(Vars_Form_Det){
    form_iteration=1
    for(i in Cols){
      if(ColsFormat[form_iteration]=="binary"){
        cat("\n")
        cat(paste0("## Description of **", as.character(i), "**:"))
        
        compDataset=na.omit(Dataset)
        
        first_value = unique(compDataset[,get(i)])[1]
        second_value = unique(compDataset[,get(i)])[2]
        
        prop_firs_value = dim(compDataset[get(i)==first_value,])[1]/n_of_observations*100
        prop_second_value = dim(compDataset[get(i)==second_value,])[1]/n_of_observations*100
        
        DF_binary=data.frame(c(first_value, second_value, NA), c(prop_firs_value, prop_second_value, df_output[2,i] ))
        cat("\n")
        print(knitr::kable(DF_binary, col.names = c("values", "Proportion")))
        cat("\n")
        
        p=ggplot(Dataset, aes_string(x=i))+
          geom_bar()+
          ggtitle(paste0("Bar graph of ",i, " defined as binary:"))
        suppressMessages(print(p))
      }
      if(ColsFormat[form_iteration]=="categorical"){
        p=ggplot(Dataset, aes_string(x=i))+
          geom_bar()+
          ggtitle(paste0("Bar graph of ",i, " defined as categorical:"))
        suppressMessages(print(p))
      }
      if(ColsFormat[form_iteration]=="continuous"){
        p1=ggplot(Dataset, aes_string(x=i))+
          geom_histogram()+
          ggtitle(paste0("Histogram of ",i, " defined as continuous:"))
        suppressMessages(print(p1))
        
        p2=ggplot(Dataset, aes_string(y=i))+
        geom_boxplot()+
        ggtitle(paste0("Box Plot of ",i, " defined as continuous:"))
        suppressMessages(print(p2))
      }
      if(ColsFormat[form_iteration]=="date"){
        p=ggplot(Dataset, aes_string(x=i))+
          geom_histogram()+
          ggtitle(paste0("Histogram of ",i, " defined as date:"))
        suppressMessages(print(p))
      }
    }
      form_iteration=form_iteration+1
    
}
```

`r if(Vars_Form_nDet){"The variables to be described and their formats are specified."}`
```{r Vars specified and Format specified and non Detailed, results = "asis", include=TRUE, echo=FALSE}
if(Vars_Form_nDet){
    form_iteration=1
    for(i in Cols){
      if(ColsFormat[form_iteration]=="binary"){
        cat("\n")
        cat(paste0("Table of **", as.character(i), "**:"))
        
        compDataset=na.omit(Dataset)
        
        first_value = unique(compDataset[,get(i)])[1]
        second_value = unique(compDataset[,get(i)])[2]
        
        prop_firs_value = dim(compDataset[get(i)==first_value,])[1]/n_of_observations*100
        prop_second_value = dim(compDataset[get(i)==second_value,])[1]/n_of_observations*100
        
        DF_binary=data.frame(c(first_value, second_value, NA), c(prop_firs_value, prop_second_value, df_output[2,i] ))
        cat("\n")
        print(knitr::kable(DF_binary, col.names = c("values", "Proportion")))
        cat("\n")
        
      }
      if(ColsFormat[form_iteration]=="categorical"){

      }
      if(ColsFormat[form_iteration]=="continuous"){

      }
      if(ColsFormat[form_iteration]=="date"){

      }
    }
      form_iteration=form_iteration+1
}
```